%-------------------------
% Resume in Latex
% Author : Mayank Thakur
% Website: https://github.com/IamMayankThakur/resume
% License : MIT
%------------------------

\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{fontawesome}
\usepackage{graphicx}
\usepackage{microtype} % for better font spacing


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{\item\small{\textbf{#1}{: #2 \vspace{-2pt}}}}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\item\small{#1: #2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=1.5em]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\newcommand{\resumeSubheadingContinue}[2]{
  \vspace{-1pt}
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

%-------------------------------------------
%%%%%%  Resume STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING-----------------
\begin{center}
  {\Huge \textbf{\scshape Mayank Thakur}}\\[4pt]
  {\normalsize
  \faEnvelope\ \href{mailto:thakurmayank88@gmail.com}{thakurmayank88@gmail.com} \,|\, 
  \faPhone\ +91 9611296430 \,|\, 
  \faLinkedin\ \href{https://linkedin.com/in/iammayankthakur}{iammayankthakur} \,|\, 
  \faGithub\ \href{https://github.com/IamMayankThakur}{IamMayankThakur}
  }
\end{center}


%-----------EXPERIENCE-----------------
\section{Work Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Akamai Technologies}{Bangalore, India (Remote)}
      {Senior II Software Engineer}{Apr 2025 - Present}
      \resumeItemListStart
        \item Developed a \textbf{SCIM client} for user life-cycle management for a Tactical \textbf{Zero Trust Access product} for the US Army
        \item Designed and developed the config deployment system for a disconnected on-prem Zero Trust Access solution 
        \item Took ownership of the Agile process as Scrum Master; led sprints, ceremonies, and releases, hiring efforts etc.
      \resumeItemListEnd


    \resumeSubheadingContinue
      {Senior Software Engineer}{Dec 2023 - Mar 2025}
      \resumeItemListStart
        \item Designed and developed the capability to rotate multiple secrets, certificates and keys throughout the system.
        \item Integrated \textbf{OIDC-based SSO} into the internal Operations Portal.
        \item Developed and maintained \textbf{control path microservices} which achieved \textbf{FedRAMP} moderate and high compliance.
        \item \textit{Tech Stack: Go, Python, Django, Celery, PostgreSQL, Redis, RMQ, Kubernetes}
      \resumeItemListEnd

    \resumeSubheading
      {Supertokens}{Mumbai, India (Remote)}
      {Backend Engineer}{Sep 2023 - Dec 2023}
      \resumeItemListStart
        \item Developed production-grade \textbf{REST APIs} and cron jobs in SaaS backend (Node.js).
        \item Maintained and improved open-source Python and Go SDKs.
        \item \textit{Tech Stack: Go, Python, MySQL, NodeJS}
      \resumeItemListEnd

    \resumeSubheading
      {Pronto}{Bangalore, India (Remote)}
      {Senior Software Engineer}{Apr 2022 - Sep 2023}
      \resumeItemListStart
        \item Designed and shipped Pronto’s \textbf{Identity Provider with OAuth, SAML}, and MFA support.
        \item Implemented authentication using SAML on custom domains.
        \item Improved logging, tracing, and overall \textbf{system's observability}.
        \item Hardened Kubernetes security by enabling mTLS with a service mesh.
        \item \textit{Tech Stack: Go, Python, FastAPI, Celery, PostgreSQL, Kubernetes}
      \resumeItemListEnd

    \resumeSubheading
      {Akamai Technologies}{Bangalore, India (Remote)}
      {Software Engineer II}{Nov 2021 - Apr 2022}
      \resumeItemListStart
        \item Developed a fully \textbf{RFC compliant SCIM server} in Go for Okta and Azure AD integration.
        \item Enabled secure service access to \textbf{RDS via AWS IAM} role-based auth.
      \resumeItemListEnd

    \resumeSubheadingContinue
      {Software Engineer}{Jan 2020 - Oct 2021}
      \resumeItemListStart
        \item Boosted test coverage with robust Python \textbf{unittests} across backend services.
        \item Developed backend APIs in django and worked on customer bug fixes
        \item \textit{Tech Stack: Go, Python, Django, Celery, PostgreSQL, Redis}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {The University of Texas at Austin}{Remote}
      {Master of Science - Computer Science}{2022 -- 2025}
    \resumeSubheading
      {PES University, Bangalore}{Bangalore, India}
      {Bachelor of Technology - Computer Science}{2016 -- 2020}
  \resumeSubHeadingListEnd

%-----------SKILLS-----------------
\section{Technical Skills}
 \resumeSubHeadingListStart
   \item \textbf{Languages}{: Python, Go, SQL, Javascript}
   \item \textbf{Frameworks}{: Django, DRF, FastAPI, Celery, Chi, Mux, pgx}
   \item \textbf{Technologies}{: AWS, Redis, PostgreSQL, Kubernetes, Docker}
   \item \textbf{Expertise}{: REST APIs, Microservices, Authentication/Authorization, Cryptography, Unit testing, Identity and Access Management, Distributed Systems, System Design, Code Reviews}
 \resumeSubHeadingListEnd

%-----------INTERESTS-----------------
\section{Interests}
    I enjoy and participate in a lot of sports, from racing marathons and Ironman triathlons to adventure sports like paragliding, scuba diving, rock climbing, and climbing big mountains in the Himalayas.

\end{document}
